Development of a permanent magnet characterisation framework for use in low-field MRI systems

### 2024-02-26 documentation/colloquium/presentation/index.qmd
added first quarto slides

## Table of Content

@@

## Software Framework

Simply tasks of data:

* data aqusition
* storage
* analysis tasks

@@

### Software Concept

test

@@

>>>>

@@

@@

##

<h1 class="r-fit-text" style="text-align: center;">MagneticReadoutProcessing</h1>

##

<h1 class="r-fit-text" style="text-align: center;">MagneticReadoutProcessing</h1>

Provides and user-oriented **open** magnetic field data hardware and software framework:

* Harware support for several magnetic field sensors
* Easy to integrate into existing projects
* Easy to extend

### Hardware Framework

### Software Framework

Simply tasks of:

* data aqusition
* data storage
* data analysis tasks

### User Interaction Points

![](images/MRP_high_level_overview.png)

### Usability Improvements

<p class="fragment">Fade in</p>
<p class="fragment fade-out">Fade out</p>
<p class="fragment highlight-red">Highlight red</p>
<p class="fragment fade-in-then-out">Fade in, then out</p>
<p class="fragment fade-up">Slide up while fading in</p>

@@

### Sensor Chraterisation
